---
title: "Erdos_renyi"
author: "Anubhav Jain"
---

## Getting started
Loading the Igraph Library
```{r}
library(igraph)
```
## Choosing the initial attributes for the model
Number of nodes in the graph
```{r}
nodes <- 10
```
Connectivity Probability
```{r}
prob <- 0.7
```

## Erdos Enyi Modelling
Making an empty graph of n nodes
```{r}
g <- make_empty_graph(n=nodes)
```

function Generate graph edges with connectivity probability p
* Take pair nodes from the graph
* Generate a random probability r
* If the generated random probability r <= connectivity p-> add an edge else ignor
* Repeat the above steps for each pair of nodes
```{r}
random_edge_generator <- function(){
  for (i in 1:(length(V(g))-1)){
    c <- i+1
    for (j in c:length(V(g))){
      if(i!=j){
        if(runif(1)<=p){
          edges <- c(edges,V(g)[i])
          edges <- c(edges,V(g)[j])
        }
      }
    }
  }
  return(edges)
}
```
Adding random edges to graph
```{r}
g<- add_edges(g, random_edge_generator())
```
## Ploting the graph
```{r}
plot.igraph(g)
```

